\problemname{Tycho}

The planetary exploration vehicle \emph{Tycho VIII} needs to get back to the home base after collecting mineral samples.
Tycho travels in a straight line from position~$0$ to the home base at position~$b$. While moving, it advances at a slow but steady pace of $1$~unit per second.
Every second, Tycho takes $1$ unit of environmental damage by the harsh planetary conditions.

The situation is made even worse by radiation from a nearby pulsar, which adds $d$ additional units of damage every $p$ seconds.
However, the radiation damage can be avoided by seeking shelter in one of the $n$ different hiding spots---caves, vegetation, large rocks, carcasses of the planet's megafauna---along the way.
Tycho can choose to stand still at any point for any integer number of seconds.

The starting position~$0$ and the home base at~$b$ are both sheltered, so Tycho takes no radiation damage there.

\medskip
What is the minumum damage Tycho will take on its journey back to the home base?

\subsection*{Input}

The first line consists of four integers $b$, $p$, $d$, and $n$, separated by single spaces:
the location $b$ of the home base,
the pulsar's flare period~$p$,
the additional radiation damage~$d$ caused by each flare of the pulsar,
the number~$n$ of the shelters.
The following $n$~lines each contain an integer giving the shelter locations $a_1$, $\ldots$, $a_n$, with 
$0<a_i< b$ for $1\leq i \leq n$ % constraint:shelterbounds
and 
$a_1<\cdots <a_n$. % constraint:sortedshelters

\subsection*{Output}

Print a single integer: the minimum amount of damage Tycho must take to reach $b$.

\subsection*{Constraints and Scoring}

You can assume
$p < b$ % constraint:pulsehappens
and
$n < b$. % constraint:sheltersfit
We always have
$1\leq b\leq 10^{12}$, % constraint:b
$0\leq d \leq 10^6$, %constraint:d
and
$0\leq n \leq 10^5$. % constraint:n

Your solution will be tested on a set of test groups, each worth a number of points.
Each test group contains a set of test cases.
To get the points for a test group you need to solve all test cases in the test group.
Your final score will be the maximum score of a single submission.

\medskip
\begin{tabular}{lll}
Group & Points & Constraints \\\hline
  $1$ & $8$  & $p\leq 10^6$ and there exists an optimal strategy, where Tycho does not wait at any position \emph{after} leaving position~$0$. \\ % constraint:nowait
  $2$ & $5$  & $b\leq 1000$, $p\leq 100$, $n\leq 10$ \\
  $3$ & $7$  & $b\leq 1000$ \\
  $4$ & $15$ & $p\leq 10^6$, $n\leq 1000$\\
  $5$ & $20$ & $p\leq 100$\\
  $6$ & $35$ & $p\leq 10^6$\\
  $7$ & $10$ & \emph{no additional constraints}
\end{tabular}

\subsection*{Example}

Consider the first sample input. The base is located at $b = 42$, the pulse happens every $p = 7$ seconds causing $d = 2$ units of radiation damage, and there are no shelters.
It is optimal for Tycho to move to the base as fast as possible. Thus, Tycho reaches the base at time $42$ and it takes $42$ units of environmental damage.
Additionaly, it takes radiation damage at times $7, 14, 21, 28, 35$. However, it doesn't take damage at time $42$ because Tycho will be at the base at this time.
In total Tycho takes $42 + 5d = 52$ damage.

Sample Inputs 2 and 3 differ only in $d$. We have $b = 15$, $p = 5$ and 3 shelters at positions $4, 9, 11$.

In Sample 2, it is optimal for Tycho to wait one second at position $0$ and move straight to the base afterwards. So it will reach the base at time $16$.
During the first two pulses at times $5$ and $10$, Tycho is sheltered at positions $4$ and $9$. But Tycho is unsheltered at time $15$ and position $14$ causing radiation damage.
In total Tycho takes $16 + d = 18$ damage.

In Sample 3, the previous strategy is no longer optimal because Tycho would take $16 + d = 20$ units of damage. If Tycho instead waits at position $11$ until time $15$, it doesn't take any radiation damage.
So the total damage is only $19$.

Note that Sample Inputs 1 and 2 are valid inputs for test group 1, but Sample Input 3 is not.